### 2016-10-06 Manuscript/SW_early_life_telomeres.Rmd
Home edits

Longitudinal data showed that early-life RTL was not related to adult RTL (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data = dd3))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data = dd3))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = dd3))$coefficients[2,4])`; Fig. 4A). Running this analysis separately for juvenile age classes revealed that this relationship was not significant for nestlings (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(dd3,Agemonths == 1)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(dd3,Agemonths == 1)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = subset(dd3,Agemonths == 1)))$coefficients[2,4])`), fledglings (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(dd3,Agemonths == 6)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(dd3,Agemonths == 6)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = subset(dd3,Agemonths == 6)))$coefficients[2,4])`) or subadults (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(dd3,Agemonths == 10)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(dd3,Agemonths == 10)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = subset(dd3,Agemonths == 10)))$coefficients[2,4])`). $\Delta$RTL was significantly lower than zero in nestlings (t = `r round2(t.test(subset(dd3,Agemonths == 1)$DeltaRTL)$statistic)`; P `r round3(t.test(subset(dd3,Agemonths == 1)$DeltaRTL)$p.value)`), but not in fledglings (t = `r round2(t.test(subset(dd3,Agemonths == 6)$DeltaRTL)$statistic)`; P = `r round2(t.test(subset(dd3,Agemonths == 6)$DeltaRTL)$p.value)`) or subadults (t = `r round2(t.test(subset(dd3,Agemonths == 10)$DeltaRTL)$statistic)`; P = `r round2(t.test(subset(dd3,Agemonths == 10)$DeltaRTL)$p.value)`), suggesting that telomere shortening was highest shortly after the nestling phase, after which both telomere shortening and telomere lengthening were observed (Fig. 4B).

>>>>

Longitudinal data showed that early-life RTL was not related to adult RTL (R^2^ = `r round2(summary(lm(RTL1~RTL+TimeDiff,data = dd3))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data = dd3))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = dd3))$coefficients[2,4])`; Fig. 4A). Running this analysis separately for juvenile age classes revealed that this relationship was not significant for nestlings (R^2^ = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 1)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 1)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL,data = subset(dd3,Agemonths == 1)))$coefficients[2,4])`), fledglings (R^2^ = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 6)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 6)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL,data = subset(dd3,Agemonths == 6)))$coefficients[2,4])`) or subadults (R^2^ = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 10)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 10)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL,data = subset(dd3,Agemonths == 10)))$coefficients[2,4])`). $\Delta$RTL was significantly lower than zero in nestlings (t = `r round2(t.test(subset(dd3,Agemonths == 1)$DeltaRTL)$statistic)`; P `r round3(t.test(subset(dd3,Agemonths == 1)$DeltaRTL)$p.value)`), but not in fledglings (t = `r round2(t.test(subset(dd3,Agemonths == 6)$DeltaRTL)$statistic)`; P = `r round2(t.test(subset(dd3,Agemonths == 6)$DeltaRTL)$p.value)`) or subadults (t = `r round2(t.test(subset(dd3,Agemonths == 10)$DeltaRTL)$statistic)`; P = `r round2(t.test(subset(dd3,Agemonths == 10)$DeltaRTL)$p.value)`), suggesting that telomere shortening was highest shortly after the nestling phase, after which both telomere shortening and telomere lengthening were observed (Fig. 4B).
